% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Samuel J. Dixon\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Contact Information} \\ Email: sdixon@posteo.net \\ Phone: (317) 450-8066}
\address{{\bf Socials} \\ Github: https://github.com/samdixon \\ Website: https://sjd.im \\
        }

\begin{resume} 
 
\section{Objective} 
generic filler section to be adjusted

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & Python, PowerShell, Bash \\

     \underline{Software:} & Windows Server, Linux, AWS, Ansible, Terraform, Packer,
                            Git, Nginx, IIS, CloudFormation, Jenkins, Docker
 \end{tabular}

 

\section{Experience}
    {\bf DevOps Engineer,} Zipari, Brooklyn, NY (Remote)\hfill Aug 2020 - Present
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Work with a team in an agile environment focused on cloud transformation, maintaining and improving existing automation, and improving developer experience.
 \item Converted existing PowerShell server automation scripts to PowerShell DSC.
 \item Developed custom PowerShell module for handling of secrets in configuration files via templating and AWS SecretsManager.
 \item Built out pipeline in Jenkins using Packer/PowerShell/AWS for automating the creation of web/auxiliary server AMIs. 
 \item Built out infrastructure as code in Runway/CloudFormation for web/auxiliary auto scaling groups.
 \item Helped drive upgrading existing QA Automation code from Python 2 to Python 3.
 \item Create, update, and maintain various Jenkins pipelines.
 \end{itemize}

 {\bf Technician,} Zionsville Community Schools, Zionsville, IN\hfill Oct 2018 - Aug 2020
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Provided end user support to all district schools.
 \item Active Directory, Office 365, and server troubleshooting as needed.
 \item Provided basic network troubleshooting.
 \item Managed over 1000 Chromebooks via Google Admin Console.
 \end{itemize}

{\bf Cloud Services Engineer,} Ahead, Chicago, IL (Remote)\hfill Jun 2018 - Oct 2018 
\begin{itemize} \itemsep -2pt %reduce space between items
\item Worked with a team focused on AWS project delivery.
\item Developed and deployed infrastructure as code.
\item Developed Python scripts for both clients and internal use.
\item Participated in on-site client workshops and knowledge transfers.
\item Created professional documentation of completed work for hand off to clients.
\end{itemize}

{\bf Associate Consultant,} Virtusa, Indianapolis, IN \hfill Jan 2016 - Jun 2018               
\begin{itemize} \itemsep -2pt
\item Worked with a team focused on managed service delivery as well as consulting and professional services.
\item Directly supported a wide variety of technologies with a focus on Microsoft, Linux, and AWS.
\item Subject matter expert of multiple client environments.
\item Created and maintained internal documentation.
\item Worked on client or monitor generated incidents with end-to-end ownership of the issue.
\item Participated in on-call rotation.
\end{itemize}

\section{Volunteer Activities} 
               {\bf Assistant Boys Cross Country Coach,} \hfill2017-2019\\
               Pendleton Heights Middle School, Pendleton, IN

\section{Education} 
A.S. in Computer Science \hfill2019 - Present\\
Ivy Tech Community College, Indianapolis, IN\\
GPA 3.7 in major, 3.55 overall\\
Dean's List, Spring 2020

\section{Certifications} 
AWS Certified Solutions Architect - Associate\hfill 2018 - 2021
 


\end{resume} 
\end{document} 
